### 2019-01-04 manuscript/manuscript.rmd
cleaned up R loose ends, reknit successfully

		sequence_matrix = 
			PartitionedMultipleAlignment( 
				phylip_path, 
				partition_path, 
				taxa, 
				partition_map_global=partition_map_global, 
				manuscript_name=manuscript_name, 
				matrix_name=matrix_name
			)

@@

```{r taxon_mapping_across_studies, eval=FALSE}

Dtaxaxman = 
	read_tsv("../reconciliation/blast/graphs/cross_mscript_taxa.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

Dtaxaxman_raw_count = nrow(Dtaxaxman)

Dtaxaxman %<>%
	distinct( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2, .keep_all = TRUE )

`r Dtaxaxman_raw_count` raw pairwise comparisons passed the similarity thresholds under these sampling criteria. These included multiple hits for the same sequence pairs from different regions. When only a single hit is retained, there are `r nrow(Dtaxaxman)` retained sequence pairs.

We next considered taxon mapping more generally.

```{r taxon_mapping, eval=FALSE}

Dtaxa = 
	read_tsv("../blast/graphs/taxon_graph.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

# Set aside species correspondense to same species in same matrix in same matrix
Dtaxa_self =
	Dtaxa %>%
		filter( mscript1 == mscript2 & dataset1==dataset2 & taxon1==taxon2  )

# Remove species correspondense to same species in same matrix in same study
Dtaxa %<>%
	filter( !(mscript1 == mscript2 & dataset1==dataset2 & taxon1==taxon2) )

n_not_self = nrow(Dtaxa)

# Remove hits in same matrix in same study
Dtaxa %<>%
	filter( !(mscript1==mscript2 & dataset1==dataset2))

# Remove hits same study, presume that taxon resolution is OK within study.
Dtaxa %<>%
	filter( !(mscript1==mscript2))

ggplot(Dtaxa) + geom_density(aes(count)) + xlim(0,50)

ggplot(Dtaxa_self) + geom_density(aes(count))

# Top of this list are candidates for renaming because they are very similar but have different names
Dtaxa %>% filter(taxon1!=taxon2) %>% arrange( desc(count))

# Top of this list are candidates for renaming because they are very different but have same names

Dtaxa %>% filter(taxon1==taxon2) %>% arrange( count )

>>>>

		# Do some cludgey renaming to make it easy to step into function below for debugging
		alignment_path = phylip_path
		partition_file = partition_path
		taxon_map_global = taxa

		sequence_matrix = 
			PartitionedMultipleAlignment( 
				alignment_path, 
				partition_file, 
				taxon_map_global, 
				partition_map_global=partition_map_global, 
				manuscript_name=manuscript_name, 
				matrix_name=matrix_name
			)

@@
